Supplementary Figures: Quality control for the target decoy approach for peptide identification

### 2022-11-14 paper_supplementary.Rmd
update figures.Rmd with graphical abstract

```{r echo=FALSE, warning=FALSE}
if (!tinytex::check_installed("achemso")) tinytex::tlmgr_install("achemso")
if (!tinytex::check_installed("caption")) tinytex::tlmgr_install("caption")
if (!tinytex::check_installed("setspace")) tinytex::tlmgr_install("setspace")
```

>>>>

```{r echo=FALSE, warning=FALSE, message=FALSE}
if (!tinytex::check_installed("achemso")) tinytex::tlmgr_install("achemso")
if (!tinytex::check_installed("caption")) tinytex::tlmgr_install("caption")
if (!tinytex::check_installed("setspace")) tinytex::tlmgr_install("setspace")
```
